[![Build Status](https://travis-ci.org/mpadge/texttimetravel.svg?branch=master)](https://travis-ci.org/mpadge/texttimetravel)
[![Project Status: Active](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

# texttimetravel

Tools for analysing temporally structured text collections

## Installation

```{r, eval=FALSE}
devtools::install_github ('mpadge/texttimetravel')
```

---------------

## Usage

Load packages and a temporally-structured corpus to work with:

```{r load, message = FALSE}
library (texttimetravel)
library (quanteda)
dat <- data_corpus_inaugural
#dat <- corpus_reshape (dat, to = "sentences") # if desired
```
(`data_corpus_inaugural` is a sample corpus from `quanteda` of inaugural speeches
of US presidents.) Then use `quanteda` functions to convert to desired tokenized
form:
```{r tokenize}
tok <- tokens (dat, remove_numbers = TRUE, remove_punct = TRUE,
               remove_separators = TRUE)
tok <- tokens_remove (tok, stopwords("english"))
```


## keywords

```{r keywords}
x <- ttt_keyness (tok, "politic*")
head (x, n = 10) %>% knitr::kable()
x <- ttt_keyness (tok, "school")
head (x, n = 10) %>% knitr::kable()
```
Note that all words associated with "school" occur only once in the corpus, and
so even though $p = 0$ in all cases, these associations can not be interpreted
as statistically meaningful.

## topics

```{r topics}
x <- ttt_fit_topics (dat, ntopics = 5)
topicmodels::get_terms(x, 10) %>% knitr::kable()
x <- ttt_fit_topics (dat, years = 1789:1900, ntopics = 5)
topicmodels::get_terms(x, 10) %>% knitr::kable()
x <- ttt_fit_topics (dat, topic = "nation", ntopics = 5)
topicmodels::get_terms(x, 10) %>% knitr::kable()
```

